---
title: "Data Mining Exercises"
author: "Keith Hultman"
date: "February 1, 2016"
output: word_document
---


# this is what i edited **************
Week 1: 2.4, 2.6, 2.8, 3.3, 3.6

2.4 a. 

```{r, echo=FALSE}
age <- c(23, 23, 27, 27, 39, 41, 47, 49, 50, 52, 54, 54, 56, 57, 58, 58, 60, 61)
percentfat <- c(9.5, 26.5, 7.8, 17.8, 31.4, 25.9, 27.4, 27.2, 31.2, 34.6, 42.5, 28.8, 33.4, 30.2, 34.1, 32.9, 41.2, 35.7)
```

```{r}
mean(age)
median(age)
sd(age)

mean(percentfat)
median(percentfat)
sd(percentfat)


```

2.4 b.

```{r}
patients <- data.frame(age, percentfat)
boxplot(x=as.list(patients), data=patients)
```

2.4 c. 
```{r}
library(ggplot2)
ggplot(patients, aes(age, percentfat)) + geom_point()

?qqplot
qqplot(patients$age, patients$percentfat, plot.it = TRUE, xlab = "Age", ylab = "Percent Fat")
```

2.6 Given two objects represented by the tuples (22, 1, 42, 10) and (20, 0, 36, 8):
(a) Compute the Euclidean distance between the two objects.
(b) Compute the Manhattan distance between the two objects.
(c) Compute the Minkowski distance between the two objects, using h = 3. 
(d) Compute the supremum distance between the two objects.

```{r}
a = sqrt((22-20)^2+(1-0)^2+(42-36)^2+(10-8)^2)
a

b = (22-20)+(1-0)+(42-36)+(10-8)
b

c = ((22-20)^3+(1-0)^3+(42-36)^3+(10-8)^3)^(1/3)
c

d = 42-36
d
```


2.8

```{r}

x = c(1.5, 2, 1.6, 1.2, 1.5)
y = c(1.7, 1.9, 1.8, 1.5, 1.0)
plot(x,y, xlim=c(1,2), ylim=c(1,2))
points(x=1.4, y=1.6, col="red")

```
Just by appearance the closest looks to be x1

Euclidean
```{r}
x[6] <- 1.4
y[6] <- 1.6
dist(as.matrix(x,y), method = "euclidean")

```
according to this, both x1 and x5 are 0.1 from new point. This doesn't look right. 

Manhattan
```{r}
dist(as.matrix(x,y), method = "manhattan", p=1)
```

Again, both x1 and x5 are closest, and matrix is identical?

Supremum by rank

x1 = 0.1
x3 = 0.2
x4 = 0.2
x2 = 0.6
x5 = 0.6

x1 is closest. 

Cosine similarity:



```{r}

```
Note that because the cosine similarity measure does not obey all of the properties of Section 2.4.4 defining metric measures, it is referred to as a nonmetric measure.
Question: which properties does it not obey?



